Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-29 prop_letter.tex
prop_letter.tex Intorduction Updating...

Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, one might argue that this resource-bounded perspective
is also crucial for understanding the very nature of physical processes.
The tension between finite precision measurement and the foundation
of quantum mechanics sharpened when Meyer~\cite{PhysRevLett.83.3751}
and Kent~\cite{Kent1999} proved the original definition of contextuality
based on infinitely precised complex numbers cannot be experimental
verified. There were a long debate about whether contextuality could
be experimental verified or not~\cite{Mermin1999,Peres2003,BarrettKent2004}.

>>>>

Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that real measurements
must be finite precision. The tension between finite precision measurement
and the foundation of quantum mechanics sharpened when Meyer~\cite{PhysRevLett.83.3751}
and Kent~\cite{Kent1999} proved the original definition of contextuality
based on infinitely precised complex numbers cannot be experimental
verified. There were a long debate about whether contextuality could
be experimental verified or not~\cite{Mermin1999,Peres2003,BarrettKent2004}.
After the debates, people are still trying to update the definition
of contextuality when they want to perform further experiment~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
